\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://danielallen.io/}{\Large Daniel Allen}} & Email : \href{mailto:dallen@danielallen.io}{dallen@danielallen.io}\\
  \href{http://danielallen.io/}{http://www.danielallen.io} %& Mobile : +447852478572 \\
\end{tabular*}

%--------SUMMARY--------------------
\section{Summary}
\small{Software engineer with industry and academic machine learning research experience. Knowledge of designing and deploying software, building and training machine learning models, and working with challenging data.}

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages and Libraries}
    {Java 17, Python, BigQuery, Tensorflow, Keras, Numpy, Pandas, Scikit, LightGBM, Bash, SQL, MATLAB, C++}
    \resumeSubItem{Technologies}{Linux, Maven, Git, Gitlab, Docker, Google Cloud, CMake}
    \resumeSubItem{Toolkit}
    {IntelliJ, VSCode, Terminal, SSH, Vim, LaTeX, 3D Slicer, ITK, ImageJ, Google Docs and Microsoft Office}
    \resumeSubItem{Skills}{Simulation, Big Data, Testing, Re-factoring, Debugging, CI/CD, Statistical Analysis, Regression, Classification, Computer Vision, Time Series, Data Visualization, Data Preparation, ML Algorithms, Principal Component Analysis (PCA), Biomedical Imaging, Teaching} 
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{Experience}
	\resumeSubHeadingListStart
		\resumeSubheading
		{Ocado Technology}{Hatfield, UK}
		{Software Engineer (E2)}{Feb. 2021 - Present}
		\resumeItemListStart
		\resumeItem{Simulation Fidelity}{Improving the accuracy and confidence in simulations of automation control systems. Built reporting systems, data objects, and event schema to analyze data from production and corresponding simulations.}
		\resumeItem{Warehouse Automation}{Implementing algorithms for new layouts and hardware. Used simulations to test and validate the performance of the warehouse with new }
		\resumeItemListEnd
    	\resumeSubheading
      	{Western University}{London, ON, Canada}
      	{Graduate Teaching Assistant}{2017 - 2019}
      	\resumeItemListStart
      	\resumeItem{Teaching Assistant - Introduction to Electrical Engineering}
      	{Course teaching engineering undergraduate students electrical circuits and electrical engineering principals. Involved running labs and grading.}
        \resumeItem{Teaching Assistant - Programming Fundamentals for Engineers}
        {Course for teaching object oriented programming to undergraduate engineering students. }
      	\resumeItemListEnd
      	\resumeSubheading
      	{McMaster University}{Hamilton, ON, Canada}
      	{NSERC USRA Research Student}{May 2014 - Aug 2014}
      	\resumeItemListStart
      	\resumeItem{Automated gait analysis}
      	{Used digital signal processing techniques on inertial measurement units to analyze and categorize patients by their walking gait.}
      	\resumeItemListEnd	

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Western University}{London, ON}
			{Masters of Engineering Science in Electrical \& Computer Engineering M.E.Sc}{ 2017 -- 2020}
    	\resumeSubheading
      		{Western University}{London, ON}
      		{Bachelor of Engineering Science in Computer Engineering B.E.Sc}{2013 -- 2017}
      		\resumeItemListStart
      		\resumeItem{University of Western Ontario Gold Medal in Computer Engineering}{Awarded for highest grade in program.}
      		\resumeItemListEnd
  	\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{LifeStyle AI}
      {Food and fitness app with multivariate time series body weight prediction using an LSTM in Tensorflow with macro nutrient and food recommendation.}
    \resumeSubItem{Automated Segmentation of Temporal Bone Structures}
      {Masters thesis on the automatic segmentation of critical anatomy within the ear for the purpose of creating 3D models for surgical simulation. Designed and implemented accurate segmentation algorithms using a variety of computer vision techniques such as multi-atlas based methods and customized convolutional neural networks.}
    \resumeSubItem{U-net for Segmentation of Lungs from CT Images}
      {A U-net convolutional neural network for segmenting lungs from the luna-16 dataset.}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-------------
\section{Key Journal Publications}
	\resumeSubHeadingListStart
		\resumeSubItem{Automated Segmentation of the Sigmoid Sinus using a Multi-Atlas Approach}{D. G. Allen et. al, 2019}
		\resumeSubItem{Multi-atlas segmentation of the facial nerve from clinical CT for virtual reality simulators}{Brad Gare, D. G. Allen, et. al, 2019}
		\resumeSubItem{Morphological analysis of sigmoid sinus anatomy: clinical applications to neurotological surgery}{Kylen Van Osch, D. G. Allen, et. al, 2019}
	\resumeSubHeadingListEnd
	  
%--------COURSEWORK------------------
%\section{Relevant Course Work}
%\small{Machine Learning, Deeplearning.ai Coursera, SQL %for Data Scientists, Data Analytics, Discrete Math, %Linear algebra, Calculus, Digital Logic, Image %Processing, Business, Statistics}

%-------------------------------------------
\end{document}